### 2020-05-21 sections/results.tex
Adds paper with measure of variability of arm pitch angles

where $\sigma_\mathrm{gal}$ is our measure of inter-arm variability of pitch angle and has a posterior distribution of $11.0^\circ\pm 0.9^\circ$. This variability is similar to the finding of \citet{2014ApJ...790...87D} and emphaises the need for fitting algorithms to not assume all arms have the same pitch angle. The spread of arm pitch angle from the mean galaxy pitch angle can be seen in Figure \ref{fig:arm-pa-spread}, with points colour-coded by the number of arms measured for a galaxy. We see a slight drop in $E[\phi_\mathrm{gal}]$ compared to $E[\phi_\mathrm{arm}]$ at small galaxy pitch angles, due to the truncation of $\phi_\mathrm{gal}$ at {0\degree}.

>>>>

where $\sigma_\mathrm{gal}$ is our measure of inter-arm variability of pitch angle and has a posterior distribution of $11.0^\circ\pm 0.9^\circ$. This variability is similar to that found by \citet{1981AJ.....86.1847K} and \citet{2014ApJ...790...87D}, and emphaises the need for fitting algorithms to not assume all arms have the same pitch angle. The spread of arm pitch angle from the mean galaxy pitch angle can be seen in Figure \ref{fig:arm-pa-spread}, with points colour-coded by the number of arms measured for a galaxy. We see a slight drop in $E[\phi_\mathrm{gal}]$ compared to $E[\phi_\mathrm{arm}]$ at small galaxy pitch angles, due to the truncation of $\phi_\mathrm{gal}$ at {0\degree}.
